### 2016-10-04 Paper_v8.tex
author ref update
minor fix

\begin{document}
\vspace*{0.35in}
\begin{flushleft}
{\Large
\textbf\newline{Population heterogeneity in the epithelial to mesenchymal transition is controlled by NFAT and phosphorylated Sp1}}
\newline
% Insert Author names, affiliations and corresponding author email.
\\
Russell Gould\textsuperscript{1},
David Bassen\textsuperscript{1},
Anirikh Chakrabarti\textsuperscript{2},
Jeffrey D. Varner\textsuperscript{2},
Jonathan Butcher\textsuperscript{1,*},
\\
\bf{1} Nancy E. and Peter C. Meinig School of Biomedical Engineering, Cornell University, Ithaca NY
\\
\bf{2} Robert Frederick Smith School of Chemical and Biomolecular Engineering, Cornell University, Ithaca, NY, USA

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
%
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
%\Yinyang These authors contributed equally to this work.

@@

\subsection*{Signaling network connectivity}
The EMT model described the gene expression program resulting from TGF$-\beta$ and VEGF-A signaling in a prototypical epithelial cell.
The TGF$-\beta$-EMT network contained 97 nodes (proteins, mRNA or genes) interconnected by 251 interactions.
The network connectivity was curated from more than 40 primary literature sources in combination with on-line databases \cite{Linding:2007fk,Jensen:2009fk}.
The model interactome was not specific to a single epithelial cell line.
Rather, we assembled canonical pathways involved in TGF$-\beta$ and VEGF-A signaling, defaulting to human connectivity when possible.
Using a canonical architecture allowed us to explore general features of TGF$-\beta$ induced EMT without cell line specific artifacts.
%On the other hand, because of the canonical architecture, we can test the model against several cell lines to test the generality of our conclusions.

>>>>

\begin{document}
\vspace*{0.35in}
\begin{flushleft}
{\Large
\textbf\newline{Population heterogeneity in the epithelial to mesenchymal transition is controlled by NFAT and phosphorylated Sp1}}
\newline
% Insert Author names, affiliations and corresponding author email.
\\
Russell Gould\textsuperscript{1,\Yinyang},
David M. Bassen\textsuperscript{1,\Yinyang},
Anirikh Chakrabarti\textsuperscript{2},
Jeffrey D. Varner\textsuperscript{2},
Jonathan Butcher\textsuperscript{1,*},
\\
\bf{1} Nancy E. and Peter C. Meinig School of Biomedical Engineering, Cornell University, Ithaca NY
\\
\bf{2} Robert Frederick Smith School of Chemical and Biomolecular Engineering, Cornell University, Ithaca, NY, USA

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
%
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
\Yinyang These authors contributed equally to this work.

@@

\subsection*{Signaling network connectivity}
The EMT model described the gene expression program resulting from TGF$-\beta$ and VEGF-A signaling in a prototypical epithelial cell.
The TGF$-\beta$-EMT network contained 97 nodes (proteins, mRNA or genes) and 169 interactions.
The network connectivity was curated from more than 40 primary literature sources in combination with on-line databases \cite{Linding:2007fk,Jensen:2009fk}.
The model interactome was not specific to a single epithelial cell line.
Rather, we assembled canonical pathways involved in TGF$-\beta$ and VEGF-A signaling, defaulting to human connectivity when possible.
Using a canonical architecture allowed us to explore general features of TGF$-\beta$ induced EMT without cell line specific artifacts.
%On the other hand, because of the canonical architecture, we can test the model against several cell lines to test the generality of our conclusions.
